Binary companions of red giant stars in \apogee\ \DR

### 2018-03-02 paper/1-catalog/twoface-catalog.tex
P-e figure

\todo{Many examples of stars that are probably unimodal}

\todo{Should figures be phase-folded?}

@@

% Notebook: HighK-unimodal
\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{highK-unimodal}
\end{center}
\caption{%
Examples of high-$K$ stars with effectively unimodal posterior samplings.
Each panel shows the data (black markers), phase-folded at the period of the
posterior sample with maximum posterior probability.
Visit velocity uncertainties are shown as black error bars (these are typically
smaller than or equal to the size of the markers), and the inferred jitter as
grey, capped error bars.
Line (blue) shows the orbit compute from the posterior sample with maximum
posterior probability.
\label{fig:highK-unimodal}
}
\end{figure}

@@

\todo{Expectation from theory? What's spectial at 10 days?}

\figurename~\ref{fig:todo} shows the orbital period and eccentricity...

@@

>>>>

@@

% Notebook: HighK-unimodal
\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{highK-unimodal}
\end{center}
\caption{%
Examples of high-$K$ stars with effectively unimodal posterior samplings and
converged MCMC samplings.
Each panel shows the data (black markers), phase-folded at the period of the
posterior sample with maximum posterior probability.
Visit velocity uncertainties are shown as black error bars (these are typically
smaller than or equal to the size of the markers), and the inferred jitter as
grey, capped error bars.
Line (blue) shows the orbit compute from the posterior sample with maximum
posterior probability.
\label{fig:highK-unimodal}
}
\end{figure}

@@

\todo{Expectation from theory? What's special at 10 days?}

\figurename~\ref{fig:unimodalPe} shows the orbital period and eccentricity...

@@

% Notebook: HighK-unimodal
\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{unimodal-P-e}
\end{center}
\caption{%
TODO:
\label{fig:unimodalPe}
}
\end{figure}
